|

### 2021-12-23 paper/dcpo_demsupport.Rmd
polish discussion of MOC

We draw two conclusions, one methodological and one substantive.
Many constructs in social science---from democracy to corruption to public opinion---are latent variables, and recent advances have made estimating them much more practicable.
As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215], without requiring any further change in modeling strategy.

@@

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are estimated with a quantifiable amount of measurement error, and measurement error can reverse the sign of estimation of coefficients [@Bound2001, 3709; @Saccenti2020, 8], attenuate or exaggerate coefficient estimates as well as bias standard errors [see, e.g., @Blackwell2017, 318-319; @caughey2018, 254].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254]. 
Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
We conduct inferences from the distributive data via the technique known as the "method of composition" (MOC) [@Tanner1993, 52].
MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
In analysis stage, uncertainty is incorporated through simulation based on variance-covariance matrix of a given model, regardless of the structures or features of the given model.
Therefore MOC can adapt any different types of models, including but not limited to different specifications for a Time-Series-Cross-Sectional approach for TSCS data [@caughey2018, A15-16], a Cox proportional hazards model [@Treier2008, 215], or individual level roll call voting model [@Kastellec2015, 791].^[For additional details on this technique, see Supplementary Information Appendix \@ref(moc).]

As an alternative way, a structural equation model(SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors [@Umeh2019], among others [@Tomarken2005].

>>>>

We draw two conclusions, one methodological and one substantive.
Many constructs in social science---from democracy to corruption to public opinion---are latent variables, and recent advances have made estimating them much more practicable.
As latent variable measurement models become more commonly used, it is absolutely necessary for researchers employing them to incorporate the associated uncertainty into their analyses.
As demonstrated here, this can be done straightforwardly using the method of composition [see @Tanner1993, 52; @Treier2008, 215], without requiring any further change in model specification.

@@

Although measurement uncertainty has not yet attracted attention in the field of comparative public opinion [see, in addition to the works examined here, @OGrady2019], latent variables are always estimated with a quantifiable amount of measurement error, and ignoring measurement error in analyses can attenuate, exaggerate, or even reverse coefficient estimates as well as bias standard errors [see, e.g., @Bound2001, 3709; @Blackwell2017, 318-319; @caughey2018, 254; @Saccenti2020, 8].
In light of this, recent studies measuring other latent variables have recommended incorporating their measurement uncertainty in analyses [see @solis_measuring_2020, 18; @Gandhi2020, 1553], and research examining the consequences of public opinion in the United States has done so [see, e.g., @Kastellec2015, 791-792; @caughey2018, 254]. 
Therefore, after replicating the original analyses that use only the point estimates for public support and the other variables included in the model, we perform the analyses again only this time incorporating uncertainty in analysis models using our replication data.
We conduct inferences from the distributive data via the technique known as the "method of composition"  [MOC, @Tanner1993, 52].
MOC accounts for uncertainty from opinion estimates and analysis models through each modeling stage.
In analysis stage, uncertainty is incorporated through simulation based on the variance-covariance matrix of a given model, regardless of its structure or features.
This allows MOC to adapt to many different types of models, including but not limited to different time-series-cross-sectional specifications [@caughey2018, A15-16], Cox proportional hazards models [@Treier2008, 215], or models of individual-level roll call voting [@Kastellec2015, 791].^[For additional details on the MOC technique, see Supplementary Information Appendix \@ref(moc).]

As an alternative way, a structural equation model (SEM) which incorporates measurement model and structural links between variables together can also account for bias caused by simultaneity between variables and measurement models.
However, SEM is a method to test the match between the model and the data, subject to confirmation bias due to the existing of competing theories which we have in the theory on democracy and public opinion, omitted variables, linear causal relationship assumption, the sensitivity to the estimator choice when both endogenous and endogenous are contaminated by measurement errors, among others [@Tomarken2005].
